### 2022-12-02 definitions.tex
details

remarque si on enlève la strong monotony:

\begin{theorem}(ref)
{\sc bounded resilience} is undecidable ??? for WSTS with upward compatibility and effective basis of $post^*$ ???
\end{theorem}

\begin{theorem}(ref)
{\sc resilience} is undecidable ??? for WSTS with upward compatibility and effective basis of $post^*$ ???
\end{theorem}

@@

si on enlève effective basis of $post^*$:

>>>>

remarque si on enlève la strong monotony mais en gardant with effective basis of $post^*$:

\begin{theorem}
{\sc bounded resilience} is undecidable ??? for WSTS with upward compatibility and effective basis of $post^*$ ???
\end{theorem}

si on garde strong mais on enlève effective basis of $post^*$:

\begin{theorem}
{\sc resilience} is undecidable for WSTS with upward compatibility ???
\end{theorem}

@@

and with effective basis of $post^*$ ???
